An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures

### 2021-05-06 CMPSpaper_writing/CMPSpaper_writing.Rmd
small edit in file, maor update of pandoc and tex

```{r, echo=FALSE, message=FALSE}
library(knitr)
library(tidyverse)
library(bulletxtrctr)

@@

```{r tiles, echo=FALSE, fig.cap="Overview of all 36 CMPS scores resulting from a bullet-to-bullet comparison of all six lands on each bullet.", out.width=".7\\textwidth", fig.align="center"}
dframe <- dframe %>% mutate(
  landA = paste0("L", landA),
  landB = paste0("L", landB),
  landB = factor(landB, levels = paste0("L", c(2:6,1))),
  bulletA = paste0("Bullet ", bulletA),
  bulletB = paste0("Bullet ", bulletB)
)

@@

\hh{XXX Could we move the code into the corresponding figure and show the relevant pieces side by side? I'm thinking of examples similar to p.38 in https://journal.r-project.org/archive/2017/RJ-2017-023/RJ-2017-023.pdf}

\begin{figure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot}The dark grey line shows the comparison signature; each red line segment shows one congruent matching profile segment.}
```{r sigplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
sig.plot <- cmps_signature_plot(
  cmps_with_multi_scale
)
sig.plot$segment_shift_plot
```
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot2}The dark grey line shows the comparison signature; the red line shows the reference signature. Solid part is the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.}
```{r sigplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
sig.plot$signature_shift_plot
```
\end{subfigure}
\caption{\label{sigplots}\hh{The resulting two figures signature plots. We need a summarizing sentence here.}}
\end{figure}

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(tidyverse)
library(bulletxtrctr)

@@

```{r tiles, echo=FALSE, fig.cap="Overview of all 36 CMPS scores resulting from a bullet-to-bullet comparison of all pairwise comparisons of the six lands on each bullet.", out.width=".7\\textwidth", fig.align="center"}
dframe <- dframe %>% mutate(
  landA = paste0("L", landA),
  landB = paste0("L", landB),
  landB = factor(landB, levels = paste0("L", c(2:6,1))),
  bulletA = paste0("Bullet ", bulletA),
  bulletB = paste0("Bullet ", bulletB)
)

@@

\begin{figure}[hbt]
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot}The dark grey line shows the comparison signature; each red line segment shows one congruent matching profile segment.}
```{r sigplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
sig.plot <- cmps_signature_plot(
  cmps_with_multi_scale
)
sig.plot$segment_shift_plot
```
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot2}The dark grey line shows the comparison signature; the red line shows the reference signature. Solid part is the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.}
```{r sigplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
sig.plot$signature_shift_plot
```
\end{subfigure}
\caption{\label{sigplots}\hh{The resulting two figures signature plots. We need a summarizing sentence here.}}
\end{figure}
